Multi-view 3D Aerosol Distribution Recovery

### 2013-07-31 article.tex
bookmark

\noindent {\bf Inverse Transform Sampling}: Monte Carlo methods
simulate probabilistic phenomena by sampling from their probability
disrtibutions.  Inverse transform sampling~\cite{devroye1986sample} is
a common method for generating sample numbers at random from any
probability distribution given its cumulative distribution function
(cdf).  Let $X$ be a random variable whose distribution can be
described by the cumulative distribution function $F$.  First we
generate a random number $u$ from the standard uniform distribution in
the interval $[0,1]$.  Then to draw a random number from the
distribution described by $F$ we need to calculate the value $x$ such
that $x = F^{-1}(u)$.

@@

\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
    section along the X-Axis of the MC simulation, Single-Scattering
    simulation and a Single-Scattering image created from the
    reconstructed distribution (\cref{sec:optimization-results}).}
  \label{fig:simulation-results1}
\end{figure}
To test the models, we simulated several atmospheric scenarios. Here
are the details:
\\

>>>>

\noindent {\bf Inverse Transform Sampling}: We use a Monte-Carlo (MC)
method as a tool for RT. MC considers scattering and attenuation as
random phenomena, that are sampled from their probability
distributions.  Sample random numbers that comply with any known
probability density function can be generated using inverse transform
sampling~\cite{devroye1986sample}. Let $u$ be a random number drawn
from a uniform distribution in the interval $[0,1]$. The number $u$
can be transformed into a random variable $X$, whose cumulative
distribution function (CDF) is $F(X)$. The transform is $X =
F^{-1}(u)$.

@@

\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/ref_images.pdf}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
    section along the X-Axis of the MC simulation, Single-Scattering
    simulation and a Single-Scattering image created from the
    reconstructed distribution (\cref{sec:optimization-results}).}
  \label{fig:simulation-results1}
\end{figure}
To test the models, we simulated several atmospheric scenarios. Here
are the details:
\\
